\documentclass{article}

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{caption, subcaption}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{float}
\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{framed}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{anyfontsize}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{abstract}
\usepackage{array}

\colorlet{LightGray}{White!90!Periwinkle}
\colorlet{LightOrange}{Orange!15}
\colorlet{LightGreen}{Green!15}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}

\declaretheoremstyle[name=Theorem,]{thmsty}
\declaretheorem[style=thmsty,numberwithin=section]{theorem}
\tcolorboxenvironment{theorem}{colback=LightGray}

\declaretheoremstyle[name=Proposition,]{prosty}
\declaretheorem[style=prosty,numberlike=theorem]{proposition}
\tcolorboxenvironment{proposition}{colback=LightOrange}

\declaretheoremstyle[name=Principle,]{prcpsty}
\declaretheorem[style=prcpsty,numberlike=theorem]{principle}
\tcolorboxenvironment{principle}{colback=LightGreen}

\setstretch{1.2}
\geometry{
    textheight=9in,
    textwidth=5.5in,
    top=1in,
    headheight=12pt,
    headsep=25pt,
    footskip=30pt
}

% ------------------------------------------------------------------------------

\begin{document}

    % Cover Page and ToC
    \include{./MainPage/cover}

    %Introduction

    \paragraph{Introduction}
    The project task consists of a binary classification problem.
    The goal is to perform fingerprint spoofing detection, i.e.\ to identify genuine vs counterfeit fingerprint images.
    The dataset consists of labeled samples corresponding to the genuine (True, label 1) class and the fake (False, label 0) class.
    The samples are computed by a feature extractor that summarizes high-level characteristics of a fingerprint
    image.
    The data is 6-dimensional.

%    Dataset Analysis


    \section{Dataset Analysis}
    \label{sec:datasetAnalysis}
    \input{./Lab/02. Lab 02/DatasetAnalysis}


%    Dimensionality Reduction


    \section{Dimensionality Reduction}
    \label{sec:dimensionalityReduction}
    \input{./Lab/03. Lab 03/DimensionalityReduction}

%    Multivariate Gaussian Density


    \section{Multivariate Gaussian Density}
    \label{sec:multivariateGaussianDensity}
    \input{./Lab/04. Lab 04/MultivariateGaussianDensity}

%    Classification Models


    \section{Model evaluation for classification}
    \label{sec:modelEvalution}
    \input{./Lab/05. Lab 05/Model evaluation for classification}


    \section{Classification Models Analysis}
    \label{sec:classificationModels}
    \input{./Lab/05. Lab 05/ClassificationModels}
    % Lab 06 NO PROJECT PART

%   Performance of Classifier
    \input{./Lab/07. Lab 07/PerformanceClassifier}

%   Logistic Regression Classifier

    \subsection{Logistic Regression Classifier}
    \label{subsec:logisticRegressionClassifier}
    \input{./Lab/08. Lab 08/LogisticRegressionClassifier}

%   Support Vector Machine Classifier
\subsection{Support Vector Machine Classifier}
\label{subsec:supportVectorMachineClassifier}
\input{./Lab/09. Lab 09/SupportVectorMachines}


%   Gaussian Mixtures Models
\section{Gaussian Mixture Models Classifier}
\label{sec:gaussianMixtureModels}
\input{./Lab/10. Lab 10/GaussianMixtureModels}

%   Calibration
% \section{Calibration}
% \label{sec:calibration}
% \input{./Lab/11. Lab 11/Calibration}


\end{document}
